Open science and the future university researcher\thanks{This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution 4.0 International License} \ccby}

### 2017-02-07 paper-imagine-new-university.tex
added ORCID and email icon

\usepackage{ccicons}

@@

\author[Kyle E.~Niemeyer]{Kyle E.~Niemeyer\thanks{
School of Mechanical, Industrial, \& Manufacturing Engineering\\
\noindent Oregon State University\\
\noindent Email: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}
}}

@@

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science. In my opinion,
the biggest barrier is that most researchers either disagree on or are unaware of
the importance (and benefits) of working openly. Since they were not trained in
doing this, e.g., during graduate school or during postdoctoral training, they
also may simply be unaware of how to research openly, or the resources that are
available to do so. Furthermore, since most of their colleagues, collaborators,
and competitors do not practice open science, no pressure comes from the
research community to change.

>>>>

\usepackage{ccicons}
\usepackage{fontawesome}
\usepackage{calc}
\newlength\myheight
\newlength\mydepth
\settototalheight\myheight{Xygp}
\settodepth\mydepth{Xygp}
\setlength\fboxsep{0pt}
\newcommand*\inlinegraphics[1]{%
  \settototalheight\myheight{Xygp}%
  \settodepth\mydepth{Xygp}%
  \raisebox{-\mydepth}{\includegraphics[height=\myheight]{#1}}%
}

@@

\author[Kyle E.~Niemeyer]{Kyle E.~Niemeyer\thanks{
School of Mechanical, Industrial, \& Manufacturing Engineering,\\
\noindent Oregon State University\\
\noindent \faEnvelopeO~\href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}\\
\noindent \inlinegraphics{orcid_128x128.png}~{\scriptsize\href{https://orcid.org/0000-0003-4425-7097}{https://orcid.org/0000-0003-4425-7097}}
}}

@@

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science. In my opinion,
the biggest barrier is that most researchers either disagree on or are unaware of
the importance (and benefits) of working openly. Since they were not trained in
doing this, e.g., during graduate school or during postdoctoral training, they
also may simply be unaware of how to research openly, or the resources that are
available to do so. Furthermore, since most of their colleagues, collaborators,
and competitors do not practice open science, no pressure comes from the
research community to change. In addition, some communities do not support or
actively oppose activities such as submitting preprints.
